---
title: "2_rmsd_plots"
output: html_document
---

```{r}
library(ggplot2)
library(dplyr)
library(viridis)

```


```{r}
#Modified snake plotter script
#Adapted from https://github.com/Yue-Jiang/snakeplotter
smoothCurve <- function(x0, x1, y0, y1, n, direction) {
  # x0: starting x
  # x1: ending x
  # y0: starting y
  # y1: ending y
  # n: number of residues
  # direction: 1 if n shape, -1 if u shape
  # draws a smooth curve between (x0, y0) and (x1, y1) with n redidues
  # returns coordinates of all residues on the smooth curve
  
  # for the middile part:
  m <- min((n %% 2 + 6), n) # number of residues in the middle part
  c <- mean(c(x0, x1))
  r <- 5 # redius used for plotting the middle part
  circ_part_x <- circ_part_y <- rep(0, m)
  for (i in 1:m) {
    circ_part_x[i] <- direction * cos(pi - i * pi / (m + 1)) * r + c
    circ_part_y[i] <- direction * sin(pi - i * pi / (m + 1)) * r
  }
  if (direction == -1) { circ_part_x <- rev(circ_part_x) }
  if (n <= m) { 
    if (direction == 1) { return(cbind(circ_part_x, circ_part_y + max(y0, y1))) }
    if (direction == -1) { return(cbind(circ_part_x, circ_part_y + min(y0, y1))) }
  }
  
  # for the side parts:
  ndiff <- round((y1 - y0) / 4) * 2 * direction
  # ndiff is even, how many more residues the left one should have than right
  na <- (n - m + ndiff) / 2
  nb <- (n - m - ndiff) / 2
  # if |ndiff| is too big: 
  if (ndiff >= n - m) {
    na <- n - m
    nb <- 0
  }
  if (ndiff < 0 && abs(ndiff) >= n - m) {
    na <- 0
    nb <- n - m
  }
  # note that n - m is even if n - m > 0

  xa <- rep(x0, na)
  xb <- rep(x1, nb)
  
  if (direction == 1) {
    top <- max(c(y0 + (na + 1) * 2, y1 + (nb + 1) * 2))
    circ_part_y <- circ_part_y + top
    ya <- seq(y0 + 2, top, length.out = na)
    yb <- seq(top, y1 + 2, length.out = nb)
  }
  if (direction == -1) {
    bottom <- min(c(y0 - (na - 1) * 2, y1 - (nb + 1) * 2))
    circ_part_y <- circ_part_y + bottom
    ya <- seq(y0 - 2, bottom, length.out = na)
    yb <- seq(bottom, y1 - 2, length.out = nb)
  }
  smtx <- c(xa, circ_part_x, xb)
  smty <- c(ya, circ_part_y, yb)

  return(cbind(smtx, smty))
} 
# plot(smoothCurve(0,20,10,-100,30,-1))

endCurve <- function(x0, y0, n, direction) {
  # x0: starting x
  # y0: starting y
  # n: number of residues
  # direction: 1 if n shape, -1 if u shape
  # draws a smooth curve starting at (x0, y0)  with n redidues
  # returns coordinates of all residues on the smooth curve
  
  r <- 5
  m <- min((n %% 2 + 6), n)
  
  xa <- rep(x0, n - m)
  ya <- rep(y0, n - m)
  for (i in seq_len(n - m)) { ya[i] <- y0 + i * direction * 2 }
  
  circ_part_x <- circ_part_y <- rep(0, m)
  for (i in seq_len(m)) {
    circ_part_x[i] <- direction * cos(pi-i*pi/(m+1)) * r  + x0 - direction*r
    circ_part_y[i] <- direction * sin(pi-i*pi/(m+1)) * r
  }
  
  if(direction==-1) {
    circ_part_y <- circ_part_y + min(c(ya, y0))
    smtx <- rev(c(circ_part_x,rev(xa)))
    smty <- rev(c(circ_part_y,rev(ya)))
  }
  if(direction==1) {
    circ_part_y <- circ_part_y + max(c(ya, y0))
    smtx <- c(circ_part_x,rev(xa))
    smty <- c(circ_part_y, rev(ya))
  }
  return(cbind(smtx, smty))
}

tmPart <- function (x0, y0, n, direction) {
  # x0: starting x
  # y0: starting y
  # n: number of residues
  # direction: 1 if top->down, -1 if down->top
  # draws the transmembrane part starting at (x0, y0)  with n redidues
  # returns coordinates of all residues on the transmembrane region
  
  tmx <- x0+rep(c(2,  0, -2,  3,  1, -1, -3),length.out=n)
  tmy <- rep(c(-2.987013e-08, -1.212121e+00, -2.424242e+00, -1.818182e+00, -3.030303e+00, -4.242424e+00, -5.454545e+00),length.out=n)
  for (i in 1:ceiling(n/7)) {tmy[(7*(i-1)+1):min(n,(7*i))] <- tmy[(7*(i-1)+1):min(n,(7*i))] - (i-1)*5.454545}
  tmy <- tmy + y0
  if (direction==-1) {tmx <- rev(tmx); tmy<-rev(tmy)}
  return(cbind(tmx,tmy))
}

tmToCenter <- function(TM, y_center) {
  diff <- mean(TM[,2]) - y_center
  TM[,2] <- TM[,2] - diff
  return(TM)
}

snakePlot <- function(ec1, tm1, ic1, tm2, ec2, tm3,
                      ic2, tm4, ec3, tm5, ic3, tm6,
                      ec4, tm7, ic4,
                      aa) {
  TM1 <- tmPart(x0=20, y0=90, n=tm1, direction=1) #TM1
  TM2 <- tmPart(x0=30, y0=90, n=tm2, direction=-1) #TM2
  TM3 <- tmPart(x0=40, y0=90, n=tm3, direction=1) #TM3
  TM4 <- tmPart(x0=50, y0=90, n=tm4, direction=-1) #TM4
  TM5 <- tmPart(x0=60, y0=90, n=tm5, direction=1) #TM5
  TM6 <- tmPart(x0=70, y0=90, n=tm6, direction=-1) #TM6
  TM7 <- tmPart(x0=80, y0=90, n=tm7, direction=1) #TM7

  y_center <- mean(c(TM1[,2], TM2[,2], TM3[,2], TM4[,2], TM5[,2], TM6[,2], TM7[,2]))

  TM1 <- tmToCenter(TM1, y_center)
  TM2 <- tmToCenter(TM2, y_center)
  TM3 <- tmToCenter(TM3, y_center)
  TM4 <- tmToCenter(TM4, y_center)
  TM5 <- tmToCenter(TM5, y_center)
  TM6 <- tmToCenter(TM6, y_center)
  TM7 <- tmToCenter(TM7, y_center)

  EC1 <- endCurve(x0=20, y0=TM1[1,2], n=ec1, direction=1) #EC1
  IC1 <- smoothCurve(x0=20, x1=30, y0=tail(TM1[, 2], 1) - 1, y1=TM2[1, 2] - 1, n=ic1, direction=-1) #IC1
  EC2 <- smoothCurve(x0=30, x1=40, y0=tail(TM2[, 2], 1), y1=TM3[1, 2], n=ec2, direction=1) #EC2
  IC2 <- smoothCurve(x0=40, x1=50, y0=tail(TM3[, 2], 1) - 1, y1=TM4[1, 2] - 1, n=ic2, direction=-1) #IC2
  EC3 <- smoothCurve(x0=50, x1=60, y0=tail(TM4[, 2], 1), y1=TM5[1, 2], n=ec3, direction=1) #EC3
  IC3 <- smoothCurve(x0=60, x1=70, y0=tail(TM5[, 2], 1) - 1, y1=TM6[1, 2] - 1, n=ic3, direction=-1) #IC3 #n.diff should be even numbers!?
  EC4 <- smoothCurve(x0=70, x1=80, y0=tail(TM6[, 2], 1), y1=TM7[1, 2], n=ec4, direction=1) #EC4
  IC4 <- endCurve(x0=80, y0=tail(TM7[, 2], 1) - 1, n=ic4, direction=-1) #IC4

  cord <- rbind(EC1, TM1, IC1, TM2, EC2, TM3, IC2, TM4, EC3, TM5, IC3, TM6, EC4, TM7, IC4)
  
  # process the text to be labeled, if aa is longer, chop it. if aa is shorter, use ''
  text <- rep('', dim(cord)[1])
  aaVec <- strsplit(aa, '')[[1]]
  for (i in seq_len(min(length(text), length(aaVec)))) {
    text[i] <- aaVec[i]
  }
  
  cordDf <- data.frame(x=cord[,1], y=cord[,2], text=text)
  return(cordDf)
}
```

# Reading in OR51_rmsd.csv from 1_OR_rmsd.ipynb 
```{r}
OR51_rmsd <- read.csv("./OR51_rmsd.csv", header=TRUE)
OR51_rmsd$X <- NULL
OR51_rmsd
```


# Creating snakeplot_df and structure for OR51 
```{r}
# creating snakeplot dataframe for OR51 sequence 
OR51_sequence = strsplit("MSINNSTSSAATFLLTGIPGLEAAHIWISIPFCFMYLIAILGNGTILFIIRTEPSLHEPMYYFLSMLAATDLGLSLSTLPTVLGIFWFNAREISFNACFAQMFFIHGFSFMESSVLLAMAFDRFVAICNPLRYASILTNTRVAKIGLAILTRSFLLILPLPFLLKRLPYCHSNVLSHSYCLHQDVMKLACADIRFNSIYGLFVVLSTMGLDSLLILFSYILILKTVLGIASREERLKALNTCVSHICAVLVFYVPMIGLSLVHRFGKHVPPVVHVLMANVYLLVPPVMNPIIYSVKTKQIRKRILRLFSLKKI", "")[[1]]

# snakePlot <- function(ec1, tm1, ic1, tm2, ec2, tm3,
#                       ic2, tm4, ec3, tm5, ic3, tm6,
#                       ec4, tm7, ic4,
#                       aa)
## base pairs of each of the following domain to form snake structure 
snakeplot_df <- snakePlot(23,28,6,29,6,34,10,22,36,30,7,33,11,19,19, paste(OR51_sequence, collapse=''))
snakeplot_df$resid <- seq(1:nrow(snakeplot_df))

# naming the domains 
snakeplot_df[1:23,"domain"] <- "N-terminus"
snakeplot_df[24:37,"domain"] <- "TMD1 Upper"
snakeplot_df[38:51,"domain"] <- "TMD1 Lower"
snakeplot_df[52:57,"domain"] <- "IC1"
snakeplot_df[58:72,"domain"] <- "TMD2 Lower"
snakeplot_df[73:86,"domain"] <- "TMD2 Upper"
snakeplot_df[87:92,"domain"] <- "EC1"
snakeplot_df[93:109,"domain"] <- "TMD3 Upper"
snakeplot_df[110:126,"domain"] <- "TMD3 Lower"
snakeplot_df[127:136,"domain"] <- "IC2"
snakeplot_df[137:147,"domain"] <- "TMD4 Lower"
snakeplot_df[148:158,"domain"] <- "TMD4 Upper"
snakeplot_df[159:194,"domain"] <- "EC2"
snakeplot_df[195:209,"domain"] <- "TMD5 Upper"
snakeplot_df[210:224,"domain"] <- "TMD5 Lower"
snakeplot_df[225:231,"domain"] <- "IC3"
snakeplot_df[232:248,"domain"] <- "TMD6 Lower"
snakeplot_df[249:264,"domain"] <- "TMD6 Upper"
snakeplot_df[265:275,"domain"] <- "EC3"
snakeplot_df[276:285,"domain"] <- "TMD7 Upper"
snakeplot_df[286:294,"domain"] <- "TMD7 Lower"
snakeplot_df[295:313,"domain"] <- "C-terminus"

# Declaring factor levels for the domain 
snakeplot_df$domain <- factor(snakeplot_df$domain, levels = c("N-terminus","TMD1 Upper","TMD1 Lower","IC1",
                                                              "TMD2 Lower","TMD2 Upper","EC1","TMD3 Upper",
                                                              "TMD3 Lower","IC2","TMD4 Lower","TMD4 Upper",
                                                              "EC2","TMD5 Upper","TMD5 Lower","IC3",
                                                              "TMD6 Lower","TMD6 Upper","EC3","TMD7 Upper",
                                                              "TMD7 Lower","C-terminus"))
snakeplot_df[grep("Upper", snakeplot_df$domain), "broad_domain"] <- 1
snakeplot_df[grep("Lower", snakeplot_df$domain), "broad_domain"] <- 2
snakeplot_df[grep("EC", snakeplot_df$domain), "broad_domain"] <- 3
snakeplot_df[grep("N-term", snakeplot_df$domain), "broad_domain"] <- 3
snakeplot_df[grep("IC", snakeplot_df$domain), "broad_domain"] <- 4
snakeplot_df[grep("C-term", snakeplot_df$domain), "broad_domain"] <- 4

snakeplot_df$broad_domain <- factor(snakeplot_df$broad_domain)

# visualize raw snakeplot structure 
ggplot(snakeplot_df, aes(x = x, y= y, label=resid)) + 
    geom_point(size = 10, stroke = 0, alpha = 0.9) +
    geom_text(hjust=0.5, vjust=0.5, color="white", size=6*0.75)

```


```{r}
## multi functional snakekeplot_ggplot function 
snake_angle_ggplot <- function(snakeplot_df, title="", min_angle=0, max_angle=80, direction = -1){
  plot <- ggplot(snakeplot_df, aes(x = x, y= y, label=text, color = CA_CX_angle)) + 
    ggtitle(title) +
    geom_path(color = "black") +
    geom_point(size = 7, stroke = 0, alpha = 0.9) +
    scale_color_viridis(name = 'angle °',
                        limits = c(min_angle,max_angle), 
                        oob = scales::squish,
                        direction = direction ) +
    geom_text(hjust=0.5, vjust=0.5, color="white", size=6*0.75) +
    theme(legend.position=c(.85,.85),
          legend.direction = "horizontal",
          legend.box = "vertical",
          legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.key.size = unit(0.7, 'cm'),
          axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          plot.title= element_text(size = 20, hjust = 0.5)) +
    guides(colour = guide_colourbar(title.position="top", title.hjust = 0.5,
                                    frame.colour = "black", ticks.color = "black"),
           size = guide_legend(title.position="top", title.hjust = 0.5))
  
  return(plot)
}


snake_distance_ggplot <- function(snakeplot_df, title="", min_distance=0, max_distance=5, direction = 1){
  # if there isn't rmsd column, color by CA_CX_distance, else color by rmsd 
  if(!is.null(snakeplot_df$rmsd)){
    plot <- ggplot(snakeplot_df, aes(x = x, y= y, label=text, color = rmsd))
  }else{
    plot <- ggplot(snakeplot_df, aes(x = x, y= y, label=text, color = CA_CX_distance))
  }
  
  plot <- plot +
    ggtitle(title) +
    geom_path(color = "black") +
    geom_point(size = 7, stroke = 0, alpha = 0.9) +
    scale_color_viridis(name = 'RMSD (Å)', 
                        limits = c(min_distance,max_distance),
                        oob = scales::squish,
                        direction = direction) +
    geom_text(hjust=0.5, vjust=0.5, color="white", size=6*0.75) +
    theme(legend.position=c(.85,.85),
          legend.direction = "horizontal",
          legend.box = "vertical",
          legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.key.size = unit(0.7, 'cm'),
          axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          plot.title= element_text(size = 20, hjust = 0.5)) +
    guides(colour = guide_colourbar(title.position="top", title.hjust = 0.5,
                                    frame.colour = "black", ticks.color = "black"),
           size = guide_legend(title.position="top", title.hjust = 0.5))
  
  return(plot)
}
## updates snakeplot_ggplot function for direction 
snake_binary_ggplot <- function(snakeplot_df, title=""){
  plot <- ggplot(snakeplot_df, aes(x = x, y= y, label=text, color = manual_direction)) + 
    ggtitle(title) +
    geom_path(color = "black") +
    geom_point(size = 7, stroke = 0, alpha = 0.9) +
    scale_color_viridis(name = ' Outwards(0) Inward (1)',
                        limits = c(0,1), oob = scales::squish ) +
    geom_text(hjust=0.5, vjust=0.5, color="white", size=6*0.75) +
    theme(legend.position=c(.85,.85),
          legend.direction = "horizontal",
          legend.box = "vertical",
          legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.key.size = unit(0.7, 'cm'),
          axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          plot.title= element_text(size = 20, hjust = 0.5)) +
    guides(colour = guide_colourbar(title.position="top", title.hjust = 0.5,
                                    frame.colour = "black", ticks.color = "black"),
           size = guide_legend(title.position="top", title.hjust = 0.5))
  
  return(plot)
}
```




# Adding rmsd feature to the snakeplot_df 
```{r}
# Adding in rmsd columns for the separate model snakeplots 
alphafold_snakeplot_df <- left_join(snakeplot_df, select(OR51_rmsd, resid, alphafold), by='resid')
colnames(alphafold_snakeplot_df)[colnames(alphafold_snakeplot_df) == 'alphafold'] <- 'rmsd'
homology_snakeplot_df <- left_join(snakeplot_df, select(OR51_rmsd, resid, pontcy), by='resid')
colnames(pontcy_snakeplot_df)[colnames(homology_snakeplot_df) == 'pontcy'] <- 'rmsd'
```

# generating a attribute .txt file for chimera plotting 
```{r}
# generating a attribute .txt file for chimera plotting 
OR51_rmsd
alphafold_rmsd_attribute <- OR51_rmsd %>%  select(resid, alphafold)
# write.table(alphafold_rmsd_attribute,"./alphafold_rmsd_attribute.txt",sep="\t",row.names=FALSE)
homology_snakeplot_df <- OR51_rmsd %>%  select(resid, pontcy)
# write.table(pontcy_rmsd_attribute,"./pontcy_rmsd_attribute.txt",sep="\t",row.names=FALSE)

```


# Plots the RMSD variance at the resid position for models in respect to CryoEM structure
```{r}
options(repr.plot.width=10, repr.plot.height=10)
snake_distance_ggplot(alphafold_snakeplot_df, title = "OR51 alphafold - cryoEM RMSD", max_distance = 5)
snake_distance_ggplot(pontcy_snakeplot_df,  title = "OR51 pontcy - cryoEM RMSD", max_distance = 5)
```


# Data from 2_OR_BindingCavity.ipynb
```{r}
OR51_CA_CX_distance <- read.csv("./OR51_CA_CX_distance.csv", header=TRUE)
OR51_CA_CX_distance$X <- NULL
OR51_CA_CX_distance

OR51_CA_CX_angle <- read.csv("./OR51_CA_CX_angle.csv", header=TRUE)
OR51_CA_CX_angle$X <- NULL
OR51_CA_CX_angle
```


# Adding CA_CX_distance/angle to the snakeplot_df 
```{r}
# Adding in distance columns for the separate model snakeplots 
alphafold_snakeplot_df <- left_join(snakeplot_df, select(OR51_CA_CX_distance, resid, alphafold), by='resid')
colnames(alphafold_snakeplot_df)[colnames(alphafold_snakeplot_df) == 'alphafold'] <- 'CA_CX_distance'
alphafold_snakeplot_df <- alphafold_snakeplot_df %>% mutate(direction = ifelse(CA_CX_distance > 0, 1, -1 )) %>% 
  filter(resid > 87)
# Adding in angle columns 
alphafold_snakeplot_df <- left_join(alphafold_snakeplot_df, select(OR51_CA_CX_angle, resid, alphafold), by='resid')
colnames(alphafold_snakeplot_df)[colnames(alphafold_snakeplot_df) == 'alphafold'] <- 'CA_CX_angle'

homology_snakeplot_df <- left_join(snakeplot_df, select(OR51_CA_CX_distance, resid, homology), by='resid')
colnames(homology_snakeplot_df)[colnames(homology_snakeplot_df) == 'homology'] <- 'CA_CX_distance'
homology_snakeplot_df <- homology_snakeplot_df %>% mutate(direction = ifelse(CA_CX_distance > 0, 1, -1 )) %>% 
  filter(resid > 87)
homology_snakeplot_df <- left_join(homology_snakeplot_df, select(OR51_CA_CX_angle, resid, homology), by='resid')
colnames(homology_snakeplot_df)[colnames(homology_snakeplot_df) == 'homology'] <- 'CA_CX_angle'

cryoEM_snakeplot_df <- left_join(snakeplot_df, select(OR51_CA_CX_distance, resid, cryoEM), by='resid')
colnames(cryoEM_snakeplot_df)[colnames(cryoEM_snakeplot_df) == 'cryoEM'] <- 'CA_CX_distance'
cryoEM_snakeplot_df <- cryoEM_snakeplot_df %>% mutate(direction = ifelse(CA_CX_distance > 0, 1, -1 )) %>% 
  filter(resid > 87)
cryoEM_snakeplot_df <- left_join(cryoEM_snakeplot_df, select(OR51_CA_CX_angle, resid, cryoEM), by='resid')
colnames(cryoEM_snakeplot_df)[colnames(cryoEM_snakeplot_df) == 'cryoEM'] <- 'CA_CX_angle'


```



```{r}
options(repr.plot.width=10, repr.plot.height=10)
snake_angle_ggplot(alphafold_snakeplot_df, title = "OR51 alphafold CA-CX angle")
snake_angle_ggplot(homology_snakeplot_df,  title = "OR51 homologyCA-CX angle")
snake_angle_ggplot(cryoEM_snakeplot_df,  title = "OR51 cryoEM CA-CX angle")

```
```{r}

options(repr.plot.width=10, repr.plot.height=10)
snake_distance_ggplot(alphafold_snakeplot_df, title = "OR51 alphafold CA-CX distance", min_distance = -5)
snake_distance_ggplot(homology_snakeplot_df,  title = "OR51 homology CA-CX distance", min_distance = -5)
snake_distance_ggplot(cryoEM_snakeplot_df,  title = "OR51 cryoEM CA-CX distance", min_distance = -5)

```

```{r}

options(repr.plot.width=10, repr.plot.height=10)
snake_distance_ggplot(alphafold_snakeplot_df, title = "OR51 alphafold CA-CX distance")
snake_distance_ggplot(homology_snakeplot_df,  title = "OR51 homology CA-CX distance")
snake_distance_ggplot(cryoEM_snakeplot_df,  title = "OR51 cryoEM CA-CX distance")

```



# Add manual data onto snakeplot_df to compare manual picked ligands vs degree 
```{r}
## manual data heat_data extracted from the modeller_plots.rmd located at modeller/OR51/.
## below are residues found to involved ( AA pointing towards binding cavity ) for the corresponding models 
alphafold_resid = strtoi(strsplit("101 104 105 108 111 180 182 183 185 186 192 199 203 206 207 251 252 255 258 259 270 274 277", " ")[[1]])
cryoEM_resid = strtoi(strsplit("100 101 104 105 108 180 182 183 195 196 199 203 207 251 252 255 259 262 273 277 280 281", " ")[[1]])
# TM7 of cryoEM 273 277 280 281
pontcy_resid = strtoi(strsplit("101 104 105 108 183 186 190 198 199 202 206 207 252 255 259 263 275 278 281", " ")[[1]])
## pontcy labeled by claire 101 104 105 108 198 199 202 206 207 252 255 259 263 275 278 281
data <- data %>% mutate( alphafold = ifelse( data$resid_number %in% alphafold_resid, 1, 0 ))
data <- data %>% mutate( cryoEM = ifelse( data$resid_number %in% cryoEM_resid, 1, 0 ))
data <- data %>% mutate( pontcy = ifelse( data$resid_number %in% pontcy_resid, 1, 0 ))
data <- data %>% filter(resid_number %in% unique(append(append(append(alphafold_resid, cryoEM_resid), pontcy_resid), c(251,252,253)))) ## filter data by resid only show up in model AND include fyg motif (251-253)
## make data
## T() swaps col and row, to transform for better horizontal heatmap plotting. 
heat_data <- t(data[,3:5])
# colnames(heat_data) <- data$resid_sequence
colnames(heat_data) <- data$resid_number
# heat_data

manual_data = data.frame(t(heat_data))[0:3]
manual_data = rownames_to_column(manual_data, var = "resid")
manual_data$resid = as.integer(manual_data$resid)
# manual_data
# attaching the manual data onto snakeplot
manual_alphafold_snakeplot_df <- left_join(snakeplot_df, select(manual_data, resid, alphafold), by='resid')
manual_alphafold_snakeplot_df <- manual_alphafold_snakeplot_df %>% filter(resid > 87)
manual_cryoEM_snakeplot_df <- left_join(snakeplot_df, select(manual_data, resid, cryoEM), by='resid')
manual_cryoEM_snakeplot_df <- manual_cryoEM_snakeplot_df %>% filter(resid > 87)
manual_homology_snakeplot_df <- left_join(snakeplot_df, select(manual_data, resid, pontcy), by='resid')
manual_homology_snakeplot_df <- manual_homology_snakeplot_df %>% filter(resid > 87)

colnames(manual_alphafold_snakeplot_df)[colnames(manual_alphafold_snakeplot_df) == 'alphafold'] <- 'manual_direction'
colnames(manual_cryoEM_snakeplot_df)[colnames(manual_cryoEM_snakeplot_df) == 'cryoEM'] <- 'manual_direction'
colnames(manual_homology_snakeplot_df)[colnames(manual_homology_snakeplot_df) == 'pontcy'] <- 'manual_direction'
```


```{r}
options(repr.plot.width=15, repr.plot.height=15)
snake_binary_ggplot(manual_alphafold_snakeplot_df, title = "OR51 alphafold manual_direction")
snake_binary_ggplot(manual_cryoEM_snakeplot_df,  title = "OR51 cryoEM manual_direction")
snake_binary_ggplot(manual_homology_snakeplot_df,  title = "OR51 homology manual_direction")

```



# plots the difference of angle/distance from CA_CX_diff.csv 
```{r}
OR51_CA_CX_diff <- read.csv("./OR51_CA_CX_diff.csv", header=TRUE)
OR51_CA_CX_diff$X <- NULL
OR51_CA_CX_diff
```


```{r}
# Adding in distance columns for the separate model snakeplots 
alphafold_diff_snakeplot_df <- left_join(snakeplot_df, select(OR51_CA_CX_diff, resid, alphafold_distance_tocryoEM), by='resid')
colnames(alphafold_diff_snakeplot_df)[colnames(alphafold_diff_snakeplot_df) == 'alphafold_distance_tocryoEM'] <- 'CA_CX_distance'
# Adding in angle columns 
alphafold_diff_snakeplot_df <- left_join(alphafold_diff_snakeplot_df, select(OR51_CA_CX_diff, resid, alphafold_angle_tocryoEM), by='resid') %>% filter(resid > 87)
colnames(alphafold_diff_snakeplot_df)[colnames(alphafold_diff_snakeplot_df) == 'alphafold_angle_tocryoEM'] <- 'CA_CX_angle'


homology_diff_snakeplot_df <- left_join(snakeplot_df, select(OR51_CA_CX_diff, resid, homology_distance_tocryoEM), by='resid')
colnames(homology_diff_snakeplot_df)[colnames(homology_diff_snakeplot_df) == 'homology_distance_tocryoEM'] <- 'CA_CX_distance'
homology_diff_snakeplot_df <- left_join(homology_diff_snakeplot_df, select(OR51_CA_CX_diff, resid, homology_angle_tocryoEM), by='resid') %>% filter(resid > 87)
colnames(homology_diff_snakeplot_df)[colnames(homology_diff_snakeplot_df) == 'homology_angle_tocryoEM'] <- 'CA_CX_angle'

```


```{r}
options(repr.plot.width=15, repr.plot.height=15)
snake_angle_ggplot(alphafold_diff_snakeplot_df, title = "OR51 alphafold CA-CX angle difference to cryoEM", max_angle = 10, direction = 1)
snake_distance_ggplot(alphafold_diff_snakeplot_df, title = "OR51 alphafold CA-CX distance difference to cryoEM", max_distance = 1)
snake_angle_ggplot(homology_diff_snakeplot_df,  title = "OR51 homology CA-CX angle difference to cryoEM", max_angle = 10, direction = 1)
snake_distance_ggplot(homology_diff_snakeplot_df,  title = "OR51 homology CA-CX distance difference to cryoEM", max_distance = 1)

```

